The first high-redshift Changing Look Quasars

### 2019-11-13 tex/CIV_CLQs.tex
continuing to update CIV_CLQs.tex

\subsection{CLQ Selection}
Our high-$z$ CLQs were identified as follows.  We selected all 64,774
SDSS DR15 sources with $z > 0.35$ classified as `QSO', having at least
two spectra separated by at least 100 days, and with a corresponding
CRTS light curve. We fitted a damped random walk to the CRTS data via
Gaussian process regression and the photometric magnitudes at the
epochs of the SDSS spectra for a given source are predicted. Those
where $|\Delta V| > 0.3$ are then selected for visual
inspection. Only three quasars SDSS J120544.7+342252.4 (hereafter
J1205+3422), SDSS J163852.93+282707.7 (hereafter J1638+2827) and SDSS
J222818.76+220102.9 (hereafter J2228+2201), satisfied these selection
criteria and showed interesting or dramatic emission line behaviour.

\begin{figure*}
  \centering
  %% trim=l b r t
  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.45cm 0.1cm, clip]
  {figures/J1205+3422_landscape_20191112.png}
  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.40cm 0.1cm, clip]
  {figures/J1638+2827_landscape_20191112.png}
  \includegraphics[width=16.7cm, trim=0.3cm 0.0cm  0.35cm 0.1cm, clip]
  {figures/J2228+2201_landscape_20191112.png}
  \vspace{-12pt}
  \caption[]{The threes high-$z$ CLQ quasars; 
    SDSS J1205+3422 (top), 
    SDSS J1638+2827 (middle), 
    SDSS J2228+2201 (bottom). 
The light curve data is present in the panels on the left hand side, with the 
spectral epoch observational timings given by the vertical lines. 
The spectra are on the right hand side, with zoom-in's on the Ly$\alpha$-\nv 
complex, the \civ\ line and the \mgii line. 
  }
  \label{fig:civ_clqs}
\end{figure*}
\subsection{Spectra}
An overview of our spectroscopic observations is given in
Table~\ref{tab:obs_notes}.  The spectra are from the SDSS
\citep{Stoughton2002, DR7, Schneider2010}, the SDSS-III Baryon
Oscillation Spectroscopic Survey \citep[BOSS][]{Eisenstein2011,
Dawson2013, Smee2013, Alam2015, Paris2017} and the SDSS-IV Extended
Baryon Oscillation Spectroscopic Survey \citep[eBOSS; ][]{Dawson2016,
Abolfathi2018, Paris2018}.  These quasars were targetted via a range
of techniques and algorithms \citep[see ][]{Richards2002, Ross2012,
Myers2015}. The SDSS, BOSS and eBOSS data are supplemented by
spectra from the Low Resolution Imaging Spectrometer (LRIS) on the 10m
Keck {\sc I} telescope \citep{Oke1995}.  and the Double Spectrograph
(DBSP) instrument on the Palomar {\it Hale} 5m telescope.

\subsection{Emission Line and Power-law slope measurements}
We use the measured quasar emission line properties from several catalogues: 
\citet{Shen2011}, \citet{Hamann2017}, \citet{Kozlowski2017} and
\citet{Calderone2017}.

\citet{Shen2011} present a compilation of properties of the 105,783
quasars in the SDSS Data Release 7 (DR7) quasar catalog \citep[DR7Q;
][]{Schneider2007}. \citet{Shen2011} report non-zero \civ\ FWHM and
EWs for approximately half (51,501) of the full DR7Q, and non-zero
\mgii FWHM and EWs for 80\% (84,183) of the DR7Q quasars).
%%
Measured line values using the methods and catalogue from
\citet{Shen2011}.  $M_{\rm I}(z=2)$ is the Absolute $i$-band magnitude
$K$-corrected to $z = 2$; Bolometric luminosity computed from the
monochromatic luminosity at 1350\AA\ using the spectral fits and
bolometric corrections (BC = 3.81) in \citet{Richards2006b}; Line
luminosity, FWHM, rest-frame equivalent width, and their errors for
the whole \civ\ profile.  Power-law slope $\alpha_{\lambda}$ for the
continuum fit for \civ; Virial BH masses using calibrations of
\citet{VestergaardPeterson2006}.  Eddington ratio computed using the
virial BH mass.

\citet{Calderone2017} present the Quasar Spectral Fitting (QSFIT)
software package which among other quantities provides luminosity
estimates as well as width, velocity offset and equivalent width of 20
emission lines, including \civ, \ciii and \mgii.  We attempt to process and fit
all nine spectra using the lastest version (v1.3.0) of the QSFIT
\href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online calculator}
and setting $E(B-V)=0.00$.
%%
The host galaxy and blended iron emission at rest-frame optical wavelengths components
are automatically disabled when they can not be constrained by the available data,
such as the case for all our objects (we do not have infrared spectral data).
%%

\citet{Hamann2017} investigate in robust detail the UV continuum and
the \civ\ (and \nv $\lambda$1238, 1242 \AA\ ) emission lines for over
200,000 quasars in BOSS DR12Q \citep{Paris2017}.  The quasar redshift
are limited to the range $1.53 \leq z \leq 5.0$ so that \civ\ and the
adjacent continuum are covered by BOSS. These measurements provide
line profile information and flux ratios\footnote{This emission-line
catalog can be downloaded from
\href{https://datadryad.org/stash/dataset/doi:10.6086/D1H59V}{here}.}
\citet{Hamann2017} was focused on $z\geq2$ quasars and specifcally
their \civ properties in order to understand the high-$z$ ``Extremely
Red Quasar'' population \citet{Ross2015, Zakamska2016, Perrotta2019,
  Zakamska2019}.  As such, we prefer the \citet{Hamann2017} emission line
values where available, though this is only for two out of our nine spectra.

When using the \citet{Shen2011} catalogue, we report line luminosity,
FWHM, rest-frame equivalent width, and their errors for the whole
\mgii profile (this catalogue also quotes values for just the broad
\mgii component, but the differences for our objects is
negligible). The line luminosities in \citet{Calderone2017} are given
in units of $10^{42}$ erg s$^{-1}$, while the line luminosities in
\citet{Shen2011} are in units of $\log(L)$.  We do not report the
\citet{Shen2011} error on the line luminosity.

Power-law continuum slopes, $\alpha$, where $f_{\lambda} \propto
\lambda^{\alpha}$, are also reported in these catalogues and from
QSFit.  We quote the most appropriate value given the emission line
wavelength.

\subsection{Multi-wavelength properties}
Mid-infrared data (3.4 and 4.6$\mu$m) is available from the beginning of the
Wide-field Infrared Survey Explorer (WISE) mission \citep[2010
January; ][]{Wright2010} through the fifth-year of NEOWISE-R
operations \citep[2018 December; ][]{Mainzer2011}. The WISE scan
pattern leads to coverage of the full-sky approximately once every six
months (a ``sky pass''), but the satellite was placed in hibernation
in 2011 February and then reactivated in 2013 October. Hence, our
light curves have a cadence of 6 months with a 32 month sampling gap.
%Radio ??

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{Overall Spectral Evolution}
Figure~\ref{fig:civ_clqs} presents the optical and infrared light
curves for three high-$z$ CLQ quasars.  Figure~\ref{fig:civ_clqs} also
shows the spectra for each epoch, with the MJD of observation given by
the dashed vertical lines in the light curves.

>>>>

\subsubsection{Mid-infrared Photometry}
Mid-infrared data (3.4 and 4.6$\mu$m) is available from the beginning
of the Wide-field Infrared Survey Explorer (WISE) mission \citep[2010
January; ][]{Wright2010} through the fifth-year of NEOWISE-R
operations \citep[2018 December; ][]{Mainzer2011}. The WISE scan
pattern leads to coverage of the full-sky approximately once every six
months (a ``sky pass''), albeit with a gap from 2011 February to 2013
October when the satellite was placed in hibernation.  Hence, our
light curves have a cadence of 6 months with a 32 month sampling
gap. \\
{\bf DS to check for any X-ray, radio etc.}

\subsection{CLQ Selection}
{\bf MJG to finalise this::} \\
Our high-$z$ CLQs were identified as follows.  We selected all 64,774
SDSS DR15 sources with $z > 0.35$ classified as `QSO', having at least
two spectra separated by at least 100 days, and with a corresponding
CRTS light curve. We fitted a damped random walk to the CRTS data via
Gaussian process regression and the photometric magnitudes at the
epochs of the SDSS spectra for a given source are predicted. Those
where $|\Delta V| > 0.3$ are then selected for visual
inspection. Only three quasars SDSS J120544.7+342252.4 (hereafter
J1205+3422), SDSS J163852.93+282707.7 (hereafter J1638+2827) and SDSS
J222818.76+220102.9 (hereafter J2228+2201), satisfied these selection
criteria and showed interesting or dramatic emission line behaviour.

\begin{figure*}
  \centering
  %% trim=l b r t
  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.45cm 0.1cm, clip]
  {figures/J1205+3422_landscape_20191112.png}
  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.40cm 0.1cm, clip]
  {figures/J1638+2827_landscape_20191112.png}
  \includegraphics[width=16.7cm, trim=0.3cm 0.0cm  0.35cm 0.1cm, clip]
  {figures/J2228+2201_landscape_20191112.png}
  \vspace{-12pt}
  \caption[]{The three high-$z$ CLQ quasars; 
    J1205+3422 (top), 
    J1638+2827 (middle) and  
    J2228+2201 (bottom). 
The light curve data is present in the panels on the left hand side, with the 
spectral epoch observational timings indicated by vertical lines. 
The spectra are on the right hand side, with zoom-in's on the Ly$\alpha$-\nv 
complex, the \civ\ line, and the \mgii line. 
  }
  \label{fig:civ_clqs}
\end{figure*}
\subsection{Spectroscopy}
An overview of our spectroscopic observations is given in
Table~\ref{tab:obs_notes}.  The spectra are from the SDSS
\citep{Stoughton2002, DR7, Schneider2010}, the SDSS-III Baryon
Oscillation Spectroscopic Survey \citep[BOSS; ][]{Eisenstein2011,
Dawson2013, Smee2013, Alam2015, Paris2017} and the SDSS-IV Extended
Baryon Oscillation Spectroscopic Survey \citep[eBOSS; ][]{Dawson2016,
Abolfathi2018, Paris2018}.  These quasars were targetted via a range
of techniques and algorithms \citep[see ][]{Richards2002, Ross2012,
Myers2015}. The SDSS, BOSS, and eBOSS data are supplemented by
spectra from the Low Resolution Imaging Spectrometer \citep[LRIS; ][]{Oke1995} on the 10m
Keck {\sc I} telescope.  and the Double Spectrograph
(DBSP) instrument on the 200'' Palomar telescope.

\subsubsection{Spectrophotometry}
{\bf MJG to finish this::} \\
We want all our spectra to have reliable flux calibrations.  SDSS
spectra ae spectrophotometrically calibrated.  BOSS and eBOSS spectra
have spectrophotometric corrections applied in the latest data release
\citep{Hutchinson2016, Jensen2016, Margala2016}.  Due to the high-$z$
of our objects, \oiii is not available to us to use as a calibrating
flux line. Instead we use photometric data from the ZTF since all our
non-SDSS/BOSS/eBOSS data are taken after MJD 57500.

\subsection{Emission Line and Power-law Slope Measurements}
We use the measured quasar emission line properties from several catalogues: 
\citet{Shen2011}, \citet{Hamann2017}, \citet{Kozlowski2017}, and
\citet{Calderone2017}.

In particular we use the Quasar Spectral Fitting (QSFIT) software
package presented in \citet{Calderone2017}. This provides luminosity
estimates as well as width, velocity offset and equivalent width of 20
emission lines, including \civ, \ciii and \mgii.  We process and fit
all nine spectra using the lastest version (v1.3.0) of the QSFIT
\href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online
calculator}.
% and setting $E(B-V)=0.00$.
%%
The host galaxy and blended iron emission at rest-frame optical
wavelengths components are automatically disabled when they can not be
constrained by the available data, such as the case for all our
objects (we do not have infrared spectral data).
%%
Power-law continuum slopes, $\alpha$, where $f_{\lambda} \propto
\lambda^{\alpha}$, are also reported in these catalogues and from
QSFit.  We quote the most appropriate value given the emission line
wavelength.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{Photometric and Spectral Evolution}
Figure~\ref{fig:civ_clqs} presents the optical and mid-IR light
curves for three high-$z$ CLQ quasars.  Figure~\ref{fig:civ_clqs} also
shows the spectra for each epoch, with the MJD of observation given by
the dashed vertical lines in the light curves.
